### 2016-12-15 Writing/draft.tex
Updates on the draft

\noindent{\Large \bf Effect of coding correlated discrete character correlation on tree inference}
\bigskip

@@

For each character, both models (HKY-binary or M$k$) where chosen randomly and ran with an overall evolutionary rate drawn from a gamma distribution ($\beta$ = $100$ and $\alpha$ = $3$).
We resimulated every invariant characters to obtain a matrix with no invariant characters.
Choosing these low evolutionary rate values allowed us to obtain discrete characters matrices with realistic values of Consistency Indices that where superior that $0.26$ \citep{OReilly20160081}.
For each trees with 25, 75 or 150 taxa we generated matrices with 100, 350 and 1000 characters following \cite{OReilly20160081}.
The matrices where generated using the \texttt{dispRity R} package \citep[][; \url{https://github.com/TGuillerme/dispRity}]{thomas_guillerme_2016_55646}.
To estimate the variance of our simulations and assess the effect of our random parameters, we repeated this step 50 times resulting in 450 morphological matrices (hereafter called the ``normal'' matrices).

@@

We inferred the topologies in both Bayesian and Parsimony using MrBayes and PAUP* respectively.
Bayesian settings.
PAUP ``settings''.

>>>>

\noindent{\Large \bf Effect of discrete character correlation on tree inference}
\bigskip

@@

For each character, both models (HKY-binary or M$k$) where chosen randomly and ran with an overall evolutionary rate drawn from a gamma distribution ($\beta$ = $100$ and $\alpha$ = $3$).
This low evolutionary rate values allowed to reduce the number of homoplasic character changes and thus reinforce the phylogenetic information in the matrices.
We resimulated every invariant characters to obtain a matrix with no invariant characters.
To ensure the that our simulation where reflecting the same parameters as real data, we only selected matrices with Consistency Indices superior to $0.26$ \citep{OReilly20160081}.

For each trees with 25, 75 or 150 taxa we generated matrices with 100, 350 and 1000 characters following \cite{OReilly20160081}.
The matrices where generated using the \texttt{dispRity R} package \citep[][; \url{https://github.com/TGuillerme/dispRity}]{thomas_guillerme_2016_55646}.
To estimate the variance of our simulations and assess the effect of our random parameters, we repeated this step 50 times resulting in 450 morphological matrices (hereafter called the ``normal'' matrices).

@@

We inferred the topologies in both Bayesian and Parsimony using MrBayes and PAUP* respectively.

Bayesian settings.

PAUP ``settings''.
